Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-02-27 size_differentiated_export.tex
Updates from Overleaf

Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics mimicking conditions int the northeast Pacific in the summertime. Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll1$). \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region. A different dynamical regime is expected to dominate during wintertime, with submesoscale dynamics playing a more important role. Submesoscale dynamics are characterized by sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km). Such dynamics are more likely to be found in the winter time, where mixed layers are deeper and lateral density gradients enhanced \citep{Thompson_2016}. The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.

@@

%TAB1
\begin{table}[t]
\caption{Summary of the key characteristics of PSOM experiments \textit{Papa\_summer} and \textit{Papa\_winter}.}
	\label{tab: meso_vs_submeso}
	\centering
 \centering
\begin{tabular}{|l|c|c|}
		\hline
											& \textit{Papa\_summer} & \textit{Papa\_winter} \\
		\hline
		Time period 								& April -- July             & January -- March          \\
		Spin-up								& 60 days                   & 50 days                   \\
		Advective timestep				    & 216 s                     & 108 s                     \\
		Horizontal diffusivity			    & 1 m$^2$/s                 & 0.2 m$^2$ s$^{-1}$        \\
		Restoration timescale			    & 3 days                    & 15 days                   \\
		Maximum M$^2$ ($\times$10$^{-8}$)	& 3.20 s$^{-2}$             & 33.9 s$^{-2}$             \\	
		Maximum N$^2$ ($\times$10$^{-4}$)	& 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\
		Initial mixed layer depth           & 73 m                      & 85 m                      \\
		Zonal wind stress                	& 0 -- 0.16 N m$^{-2}$      & -0.05 -- 0.17 N m$^{-2}$  \\	
		Surface heat flux               	& -46.8 -- 167.5 W m$^{-2}$ & -57.6 -- 15.3 W m$^{-2}$  \\	
		\hline
	\end{tabular}
\end{table}

@@

To ensure that PSOM simulations yielded realistic conditions for both \textit{Papa\_summer} and \textit{Papa\_winter}, distributions of horizontal ($M^2$) and vertical ($N^2$) buoyancy gradients are compared with glider observations collected over the period 2008-2009 \citep{Pelland_2016}.

During this period, underwater gliders sampled in a ``bow-tie" pattern centered on Station Papa. Gliders sample the water column following a triangular wave, whose shape is easily affected by currents, due to the slow moving speed of the glider ($\sim$1 km/hr). It is therefore challenging to associate a specific spatial scale with gradients computed between glider profiles, as profile separation distances can be highly variable through depth and time. To circumvent this issue, horizontal buoyancy gradients are computed between each pair of glider profiles available within one branch of the bow-tie. Each along-track buoyancy gradient is then associated with a separation scale and a timestamp.

 Glider-based density gradients are highly affected by internal waves. To filter the impact of internal waves on the PDF of horizontal buoyancy gradients, only gradients computed at a scale of $\pm$ 1 km of twice the Rossby radius are considered. Rossby radii are $\sim 8$ km in winter and $\sim 20$ km in summer.

@@

\begin{equation}
x_{t_1} = \left(x_0 + \frac{\delta}{\beta}\right)\exp^{-\beta(t_1 - t_0)} - \frac{\delta}{\beta}
\label{eq: PT_advection}
\end{equation}
The time it will take for the particle to reach the eastern or western face of the grid cell can be computed by taking $x_{t_1} = x_i$ or $x_{t_1} = x_{i-1}$, respectively, and solving for $t_1$. For each advective timestep, the times required for the particle to reach any of the 6 walls of the grid cell are computed using Equation \ref{eq: PT_advection}. If any of those times is shorter than the advective timestep, the particle is advected until it reaches the cell wall. Then the flow field in the adjacent grid cell is considered and the particle is advected over the remaining time. For each particle tracking experiment, four different classes of particles were released. Each particle class is characterized by a different sinking velocity: 0.025, 0.05, 1, and 5 m/day. The slowest-sinking class was essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported through gravitational sinking, a timescale much greater than commonly observed remineralization timescales. The fastest-sinking velocity is chosen as a low end-member representing velocity classes that will be exported in its entirety over the course of our experiment. The results presented for the 5 m/day sinking class can therefore be extrapolated to any class with a higher sinking velocity.

In the horizontal, particles are seeded once every 250 m over the entire domain in the x-direction, and for 100 $<y<$ 200 km in the y-direction. The seeding is centered on the position of the middle front (see Figure \ref{fig: Papa_summer}) and is therefore not affected by artificial features developing at the solid north and south boundaries. In the vertical, eleven of those sheets of particles are seeded every 1 m between 75 and 85 m. This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined as the 1\% light level. The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically Available Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}. The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \citep{Sherry_1999,Harrison_2004}.

The particle advective timestep is set to 1.5 hours. The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}. Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity). Particles are tracked for three weeks (28 days). Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles. Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-suspended into the mixed layer. %The export horizon is therefore set to 100 m, based on the seasonal cycle observed at Station Papa \citep{Pelland_2016}.

@@

\begin{equation}
N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}
\label{eq: powerlaw_radius}
\end{equation}
where $N_0$ and $r_0$ represent a reference particle number and radius, and are chosen arbitrarily. For small particles ($<400\mu m$) and relatively cold temperature ($<15^oC$), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ tend to follow Stokes law, with $w_s \propto r^2$ \citep{Bach_2012}. \cite{Bach_2012} also demonstrates that Stokes law is generally a lower-bound limit to estimate sinking velocities for a specific particle size. Assuming a Stokes-like relationship, Equation \ref{eq: powerlaw_radius} can thus be re-written in terms of sinking velocities:

\begin{equation}
N(w_s) = N_0 \left(\frac{w_s}{w_{s_0}}\right)^{-\xi/2}
\label{eq: powerlaw_velocity}
\end{equation}
For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can thus be computed using Equation \ref{eq: powerlaw_velocity} (See Figure \ref{fig: sinking_velocity_spectrum}). For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represent 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}). The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$, can be estimated if the biomass is assumed to vary with the particle's volume. The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed using:

% FIG4
\begin{figure}[ht]
	\centering
	\includegraphics[width = .6\linewidth]{figures/Fig4_particle_PDF}
	\caption{Normalized number of particles (solid) and biomass (dashed) to the fastest-sinking particle class. Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 0 (black), and 2 (blue).}
	\label{fig: sinking_velocity_spectrum}
\end{figure}

\begin{equation}
	B_p(w_s) = B_p(w_{s_0})\left(\frac{w_s}{w_{s_0}}\right)^{3/2}
	\label{eq: biomass_realparticle}
\end{equation}
where $B_p(w_{s_0})$ is a reference biomass of one particle in the sinking velocity class $w_{s_0}$. The total biomass associated with one simulated particle can be obtained by scaling Equation \ref{eq: biomass_realparticle} by the ratio $N(w_s)/N_0$:

\begin{equation}
	B(w_s) =  B_0\left(\frac{w_s}{w_{s_0}}\right)^{3/2}\frac{N(w_s)}{N_0}
	\label{eq: biomass_simulatedparticle}
\end{equation}
where $B_0 = B_p(w_{s_0})$. Combining Equations \ref{eq: powerlaw_velocity} and \ref{eq: biomass_simulatedparticle} yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
\begin{equation}
	B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}
	\label{eq: biomassjungeslope}
\end{equation}
Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}). This normalized formulation of particle number and biomass (Equations \ref{eq: powerlaw_velocity} and \ref{eq: biomassjungeslope}) presents the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments. For the purpose of this study, only the relative amount of biomass is relevant. For simplicity, we therefore define a normalized biomass unit as $B_0=$ 1.

\subsubsection{Particle Remineralization Scheme}
\label{sec: remin_scheme}
Remineralization of particles as they sink through the water column evidently impact the export of biomass. Slow-sinking particles therefore are subject to shallower remineralization than fast-sinking particles. In this study, the impact of remineralization is considered through the implementation of a time-dependent sinking velocity. Remineralization processes driving remineralization rates are complex, species-dependent, and generally not well-understood. In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship linking carbon content and time. This implicitly assumes that the biomass content of a particle diminishes in time proportionally to the particle volume. Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}:
\begin{equation}
	B (t) = B^0\exp(-kt)
	\label{eq: remin_scheme}
\end{equation}
where $B^0$ denotes the biomass content at $t = 0$ days, and $k = 0.13$ day$^{-1}$. This remineralization rate determined by \cite{Iversen_2010} is independent of particle sinking velocity, and seems to generally agree with other findings, despite the large uncertainties \citep{Ploug_2008, Iversen_2013}. The change in biomass with time is in turn expected to affect the sinking velocity of the particle. Given that $B \propto w^{3/2}$ (see Equation \ref{eq: biomass_realparticle}),  a time-varying sinking velocity is imposed to particles in all sinking-velocity classes using:

\begin{equation}
w_s (t) = w_s^0\exp(-\frac{2kt}{3})
\label{eq: sinking_velocity_remin}
\end{equation}
where $w_s^0$ is the initial sinking velocity at $t = 0$ days. Particles are classified based on their initial sinking-velocity. However, it is worth noting that over the length of the particle-tracking experiments including remineralization (28 days), particles slow down by more than 90\% of their initial velocity.

\section{Results}
\label{sec: Results}
\subsection{Physical model}

Two model experiments are designed to capture different dynamical conditions observed in the northeast Pacific Ocean in summer and winter. \textit{Papa\_summer} is initialized in early spring (doy 105) when the water column is characterized by a relatively deep mixed layer ($\sim$100 m) and a halocline present between 100 and 150 m (Figure \ref{fig: Papa_summer}). The forcing by a realistic, positive, net heat flux generates the restratification of the water column, with the development of a strong thermocline between 25 and 50 m leading to the shoaling of the mixed layer and a subsurface peak in $N^2$ at about 30 m (see Figure \ref{fig: Papa_summer}). A comparison between model outputs and monthly-averaged density profiles from underwater gliders collected in June and July over the period 2008-2009 yields correlation coefficients of $r = 0.87$ and $r = 0.88$, respectively. These correlation coefficients suggest that \textit{Papa\_summer} captures reasonably well the vertical spring and summer conditions in the northeast Pacific Ocean.

In the horizontal, the prescribed density fronts progressively become unstable within the first 60 days of the experiment (Figure \ref{fig: Papa_summer}). During this time, the Total Kinetic Energy (TKE) contained in the model domain slowly increases before reaching a maximum at doy 162, where it remains relatively constant for the rest of the simulation. The flattening of the TKE curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments. The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=( \partial v/ \partial x - \partial u/ \partial y)/f$; Figure \ref{fig: dynamics}).

%FIG5
\begin{figure}[t]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig5_dynamic_signature_w_valid}
	\caption{Snapshots of $M^2$ (top), $\zeta /f$ (middle), and $w$ (bottom) half-way through the particle tracking experiment for \textit{Papa\_summer} (left and blue) and \textit{Papa\_winter} (right and red), with the Mixed Layer Depth indicated by the solid black line. The corresponding Probability Distribution Functions (PDFs) are shown in the center. Note the changing color scales between \textit{Papa\_summer} and \textit{Papa\_winter}. Histograms of M$^2$ computed from glider data at Station Papa in February (blue line) and July (red line) are superimposed in the top middle panel.}
	\label{fig: dynamics}
\end{figure}

The largest horizontal buoyancy gradients are observed above the thermocline ($z<$50 m) and along the halocline (100-200 m), and range between 0 and 1.2$\times 10^{-7}$ s$^{-2}$ (Figure \ref{fig: dynamics}). These relatively weak density gradients result in low Rossby numbers O(0.1), positive on the denser (north) side of the front, and negative on the lighter (south) side of the front. Corresponding vertical velocities are consistently weaker than 1 m/day ($<$10$^{-5}$ m/s) and are characterized by regions of weak upwelling and downwelling on the order of 10 km, associated with the meandering of the front \citep{Bower_1989}. Alternating bands of upwelling and downwelling at $\mathcal{O}$(1 km) spatial scale are superimposed, likely caused by propagating internal waves. Coherent vertical velocities structures are homogeneous to depths much greater than the mixed layer depth ($\sim$25 m; Figure \ref{fig: Papa_summer}). The amplitude of the vertical velocity field coincides with the expected order of magnitude given by the scaling $w \propto RofU/N$ \citep{Mahadevan_2016}: using $Ro\sim0.1$ (Figure \ref{fig: dynamics}), $N\sim10^{-2}$ 1/s (Figure \ref{fig: Papa_summer}), $f\sim10^{-5}$ 1/s, and $U\sim0.01$ m/s, we obtain $w\sim 10^{-6}$ m/s. The agreement between the scaling and the model outputs suggest that PSOM is capable of reproducing a realistic vertical flow field.

\textit{Papa\_winter} is, on the other hand, initialized in the winter (doy 0) with the objective to capture a time period where the mixed layer depth is deeper ($\sim$ 100 m) and density gradients more pronounced \citep{Pelland_2016}. At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m. After spin-up, the vertical stratification remains consistent throughout the model run, and compares well to the vertical profile obtained from glider observations for the month of March ($r = 0.95$; see Figure \ref{fig: Papa_winter}). In the horizontal, prescribed density fronts are much sharper than in \textit{Papa\_summer} (O(1 km ) vs. O(10 km)). Because of these stronger density gradients, combined with the alternating zonal winds and constantly negative surface heat flux, the fronts become unstable more rapidly than in \textit{Papa\_summer} (Figure \ref{fig: Papa_winter}). As a result, TKE starts to plateau at doy 48. The experiment is considered spun-up by doy 50 and the particle-tracking experiment is initialized. %Many sharp fronts and filaments on the order of 1 km can be seen in \textit{Papa\_winter}, penetrating to ocean upper layer to the deeper than in the summer, dissipating within the mixed layer at $\sim$100 m (Figure \ref{fig: dynamics}).

>>>>

Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics mimicking conditions int the northeast Pacific in the summertime. Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll$1). \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region. A different dynamical regime is expected to dominate during wintertime, with submesoscale dynamics playing a more important role. Submesoscale dynamics are characterized by sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km). Such dynamics are more likely to be found in the winter time, where mixed layers are deeper and lateral density gradients enhanced \citep{Thompson_2016}. The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.

@@

%TAB1
\begin{table}[t]
\caption{Summary of the key characteristics of PSOM experiments \textit{Papa\_summer} and \textit{Papa\_winter}.}
	\label{tab: meso_vs_submeso}
	\centering
 \centering
\begin{tabular}{|l|c|c|}
		\hline
											& \textit{Papa\_summer} & \textit{Papa\_winter} \\
		\hline
		Time period 								& April -- July             & January -- March          \\
		Spin-up								        & 60 days                   & 50 days                   \\
		Advective timestep				            & 216 s                     & 108 s                     \\
		Horizontal diffusivity			            & 1 m$^2$ s$^{-1}$          & 0.2 m$^2$ s$^{-1}$        \\
		Restoration timescale			            & 3 days                    & 15 days                   \\
		Maximum initial M$^2$ ($\times$10$^{-8}$)	& 3.2 s$^{-2}$             & 33.9 s$^{-2}$             \\	
		Maximum initial N$^2$ ($\times$10$^{-4}$)	& 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\
		Initial mixed layer depth                   & 73 m                      & 85 m                      \\
		Zonal wind stress                	        & 0 -- 0.16 N m$^{-2}$      & -0.05 -- 0.17 N m$^{-2}$  \\	
		Surface heat flux               	        & -46.8 -- 167.5 W m$^{-2}$ & -57.6 -- 15.3 W m$^{-2}$  \\	
		\hline
	\end{tabular}
\end{table}

@@

To ensure that PSOM simulations yielded realistic conditions for both \textit{Papa\_summer} and \textit{Papa\_winter}, distributions of horizontal ($M^2$) and vertical ($N^2$) buoyancy gradients are compared with glider observations collected over the period 2008-2009 \citep{Pelland_2016}.
During this period, underwater gliders sampled in a ``bow-tie" pattern centered on Station Papa. Gliders sample the water column in a triangular wave pattern, whose shape is easily affected by currents, due to the slow moving speed of the glider ($\sim$1 km/hr). It is therefore challenging to associate a specific spatial scale with gradients computed between glider profiles, as profile separation distances can be highly variable through depth and time. To circumvent this issue, horizontal buoyancy gradients are computed between each pair of glider profiles available within one branch of the bow-tie. Each along-track buoyancy gradient is thus associated with a specific separation scale and a timestamp. Glider-based density gradients can be affected by internal waves. To filter the impact of internal waves on the PDF of horizontal buoyancy gradients, only gradients computed at a scale of twice the Rossby radius $\pm$ 1 km are considered. Rossby radii are $\sim 8$ km in winter and $\sim 20$ km in summer.

@@

\begin{equation}
x_{t_1} = \left(x_0 + \frac{\delta}{\beta}\right)\exp^{-\beta(t_1 - t_0)} - \frac{\delta}{\beta}
\label{eq: PT_advection}
\end{equation}
The time it will take for the particle to reach the eastern or western face of the grid cell can be computed by taking $x_{t_1} = x_i$ or $x_{t_1} = x_{i-1}$, respectively, and solving for $t_1$. For each advective timestep, the times required for the particle to reach any of the 6 walls of the grid cell are computed using (\ref{eq: PT_advection}). If any of those times is shorter than the advective timestep, the particle is advected until it reaches the cell wall. Then the flow field in the adjacent grid cell is considered and the particle is advected over the remaining time.

\subsubsection{Particle Seeding}

For all particle-tracking experiments, a single particle seeding event is prescribed. In the horizontal, particles are seeded every 250 m over the entire domain in the x-direction, and for 100 $<y<$ 200 km in the y-direction. The seeding is centered over the mean position of the middle front (see Figure \ref{fig: Papa_summer}) and is therefore not affected by undesired effects created by the solid north-south solid boundaries. In the vertical, particles are seeded every 1 m between 75 and 85 m. This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined by the 1\% light level. The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically Available Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}. The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \citep{Sherry_1999,Harrison_2004}.

In each particle-tracking experiment, four different classes of particles are released. Each particle class is characterized by a different sinking velocity: 0.025, 0.05, 1, and 5 m/day. The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales. The fastest-sinking velocity is chosen as a low end-member representing velocity classes that will be exported in its entirety over the course of our experiment. The results presented for the 5 m/day sinking class can therefore be extrapolated to any class with a higher sinking velocity.

The advective timestep for particles is set to 1.5 hours. The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}. Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity). Particles are tracked for three weeks (28 days). Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles. Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-suspended into the mixed layer. %The export horizon is therefore set to 100 m, based on the seasonal cycle observed at Station Papa \citep{Pelland_2016}.

@@

\begin{equation}
N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}
\label{eq: powerlaw_radius}
\end{equation}
where $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily. For small particles ($<$400$\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ tend to follow Stokes law, with $w_s \propto r^2$ \citep{Bach_2012}. \cite{Bach_2012} also demonstrate that Stokes law is generally a lower-bound estimate of sinking velocities for a specific particle size. Assuming a Stokes-like relationship, (\ref{eq: powerlaw_radius}) can be re-written in terms of sinking velocities as:

\begin{equation}
N(w_s) = N_0 \left(\frac{w_s}{w_{s_0}}\right)^{-\xi/2}
\label{eq: powerlaw_velocity}
\end{equation}
For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can thus be computed using (\ref{eq: powerlaw_velocity}) (See Figure \ref{fig: sinking_velocity_spectrum}). For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represent 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}). The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$, can be estimated if the biomass is assumed to vary with the particle's volume. The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed using:

% FIG4
\begin{figure}[ht]
	\centering
	\includegraphics[width = .6\linewidth]{figures/Fig4_particle_PDF}
	\caption{Normalized number of particles (solid) and biomass (dashed) to the fastest-sinking particle class. Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 3 (black), and 2 (blue).}
	\label{fig: sinking_velocity_spectrum}
\end{figure}

\begin{equation}
	B_p(w_s) = B_p(w_{s_0})\left(\frac{w_s}{w_{s_0}}\right)^{3/2}
	\label{eq: biomass_realparticle}
\end{equation}
where $B_p(w_{s_0})$ is a reference biomass of one particle in the sinking velocity class $w_{s_0}$. The total biomass associated with one simulated particle can be obtained by scaling (\ref{eq: biomass_realparticle}) by the ratio $N(w_s)/N_0$:

\begin{equation}
	B(w_s) =  B_0\left(\frac{w_s}{w_{s_0}}\right)^{3/2}\frac{N(w_s)}{N_0}
	\label{eq: biomass_simulatedparticle}
\end{equation}
where $B_0 = B_p(w_{s_0})$. Combining (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomass_simulatedparticle}) yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
\begin{equation}
	B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}
	\label{eq: biomassjungeslope}
\end{equation}
Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}). This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) presents the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments. For the purpose of this study, only the relative amount of biomass is relevant. For simplicity, we therefore define a normalized biomass unit as $B_0=$ 1.

\subsubsection{Particle Remineralization Scheme}
\label{sec: remin_scheme}
Remineralization of particles as they sink through the water column evidently impacts the export of biomass. Slow-sinking particles therefore are subject to shallower remineralization than fast-sinking particles. In this study, the impact of remineralization is considered through the implementation of a time-dependent sinking velocity. Remineralization processes driving remineralization rates are complex, species-dependent, and generally not well-understood. In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship linking carbon content and time. This implicitly assumes that the biomass content of a particle decreases in time proportionally to the particle volume. Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}:
\begin{equation}
	B (t) = B^0\exp(-kt)
	\label{eq: remin_scheme}
\end{equation}
where $B^0$ denotes the biomass content at $t = 0$ days, and $k = 0.13$ day$^{-1}$. This remineralization rate determined by \cite{Iversen_2010} is independent of particle sinking velocity, and seems to generally agree with other findings, despite the large uncertainties \citep{Ploug_2008, Iversen_2013}. The change in biomass with time is in turn expected to affect the sinking velocity of the particle. Given that $B \propto w^{3/2}$ (see Equation (\ref{eq: biomass_realparticle})), particles in all sinking-velocity classes undergo a decay in sinking speed according to:

\begin{equation}
w_s (t) = w_s^0\exp(-\frac{2kt}{3})
\label{eq: sinking_velocity_remin}
\end{equation}
where $w_s^0$ is the initial sinking velocity at $t = 0$ days. Particles are classified based on their initial sinking-velocity. However, it is worth noting that over the length of the particle-tracking experiments that include remineralization (28 days), particle sinking speeds slow down to 10\% of their initial velocity.

\section{Results}
\label{sec: Results}
\subsection{\fixme{Seasonal change in dynamical regime? or seasonal cycle in submesoscale activity?}}

Two model experiments are designed to capture different dynamical conditions observed in the northeast Pacific Ocean in summer and winter. \textit{Papa\_summer} is initialized in early spring (doy 105) when the water column is characterized by a relatively deep mixed layer ($\sim$100 m) and a halocline located between 100 and 150 m (Figure \ref{fig: Papa_summer}). The forcing by a realistic, positive, net heat flux generates the restratification of the water column, with the development of a strong thermocline between 25 and 50~m leading to the shoaling of the mixed layer and a subsurface peak in $N^2$ at about 30 m (see Figure \ref{fig: Papa_summer}). A comparison between model outputs and monthly-averaged density profiles from underwater gliders collected in June and July over the period 2008-2009 yields correlation coefficients of $r = 0.87$ and $r = 0.88$, respectively. These high correlation suggest that \textit{Papa\_summer} numerical experiment captures the vertical spring and summer conditions in the northeast Pacific Ocean.

In the horizontal, the prescribed density fronts progressively become unstable within the first 60 days of the experiment (Figure \ref{fig: Papa_summer}). During this time, the Total Kinetic Energy (KE$_{\text{tot}}$) contained in the model domain slowly increases before reaching a maximum at doy 162, where it remains relatively constant for the rest of the simulation. The flattening of the KE$_{\text{tot}}$ curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments. The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=(v_x - u_y)/f$ where f = 1.12$\times10^{-4}$; Figure \ref{fig: dynamics}).

%FIG5
\begin{figure}[t]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig5_dynamic_signature_w_valid}
	\caption{Snapshots of $M^2$ (top), $\zeta /f$ (middle), and $w$ (bottom) half-way through the particle tracking experiment for \textit{Papa\_summer} (left) and \textit{Papa\_winter} (right), with the Mixed Layer Depth indicated by the solid black line. The corresponding Probability Distribution Functions (PDFs) are shown in the center for both \textit{Papa\_summer} (blue) and \textit{Papa\_winter} (red). Note the different colorbars used for \textit{Papa\_summer} and \textit{Papa\_winter}. Histograms of M$^2$ computed from glider data at Station Papa in February (blue line) and July (red line) are superimposed in the top middle panel.}
	\label{fig: dynamics}
\end{figure}

%The largest horizontal buoyancy gradients are observed above the thermocline ($z$$<$50 m) and along the halocline (100--200 m), and range between 0 and 1.2$\times 10^{-7}$ s$^{-2}$ (Figure \ref{fig: dynamics}). 
Lateral buoyancy gradients in the summer are relatively weak $\mathcal{O}$(10$^{-8}$ s$^{-2}$) and result in low Rossby numbers $\mathcal{O}$(0.1), with positive relative vorticity on the denser (north) side of the front and negative relative vorticity on the lighter (south) side of the front. Corresponding vertical velocities are consistently weaker than 1 m/day ($<$10$^{-5}$ m/s) and are characterized by regions of weak upwelling and downwelling on 10 km scales, associated with the meandering of the front \citep{Bower_1989}. Alternating bands of upwelling and downwelling at $\mathcal{O}$(1 km) spatial scale are superimposed, and likely caused by propagating internal waves. Coherent vertical velocities structures extend to depths much greater than the mixed layer depth ($\sim$25 m; Figure \ref{fig: dynamics}). The amplitude of the vertical velocity field coincides with the expected order of magnitude given by the scaling $w \propto RofU/N$ \citep{Mahadevan_2016}: using $Ro\sim0.1$ (Figure \ref{fig: dynamics}), $N\sim10^{-2}$ 1/s (Figure \ref{fig: Papa_summer}), $f\sim10^{-5}$ 1/s, and $U\sim0.01$ m/s, we obtain $w\sim 10^{-6}$ m/s. %The agreement between the scaling and the model outputs suggest that PSOM is capable of reproducing a realistic vertical flow field.

\textit{Papa\_winter} is, on the other hand, initialized in the winter (doy 0) to capture a time period where the mixed layer depth is deeper ($\sim$ 100 m) and density gradients more pronounced \citep{Pelland_2016}. At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m \citep[Figure \ref{fig: Papa_winter}][]{Pelland_2016}. After spin-up, the vertical stratification remains consistent throughout the model run, and compares well to the vertical profile obtained from glider observations for the month of March ($r = 0.95$; see Figure \ref{fig: Papa_winter}). In the horizontal, prescribed density fronts are much sharper than in \textit{Papa\_summer} (O(1 km ) vs. O(10 km)). Because of these stronger density gradients, combined with the alternating zonal winds and constantly negative surface heat flux, the fronts become unstable more rapidly than in \textit{Papa\_summer} (Figure \ref{fig: Papa_winter}). As a result, KE$_{\text{tot}}$ starts to plateau at doy 48. The experiment is considered spun-up by doy 50 and the particle-tracking experiment is initialized. %Many sharp fronts and filaments on the order of 1 km can be seen in \textit{Papa\_winter}, penetrating to ocean upper layer to the deeper than in the summer, dissipating within the mixed layer at $\sim$100 m (Figure \ref{fig: dynamics}).
